---
title: "dsproject"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dsproject}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
**Overview**

The goal of dsproject is to provide a fast and friendly way to create a project, load/attach packages, read data from a file in a dataframe. It is designed to flexibly read many types of data files used, and it is made friendly for users to import a file by prompting the user to choose a file.

**Usage**

Install package with:

```{r, eval=FALSE}

# The easiest way to get dsproject is to install it from the development version from GitHub:
if(!require(devtools)){
  install.packages("devtools")
}

devtools::install_github("aaldarmaki9/dsproject")

```
Load dsproject with:

```{r, eval=FALSE}
library(dsproject)
```

**Read a File with import Function**


To read a dataset with dsproject you can do it in two ways: using the **import** function that includes the filepath, or run the **import** function and it will prompt you to choose a file. 

Import function supports six file types:

1. Stata dta files.
2. Spss sav files.
3. Excel xlsx files.
4. Excel xls files.
5. General delimited files.

In many cases, this function will just work: you supply the path to a file or choose a file and you get a dataframe back. The following example loads a sample file with **import** function:

```{r, eval=FALSE}
mtcars <- import("mtcars.xlsx")
```

**Create a Project with make_project Function**


To create a project with dsproject you can do it by using the **make_project** function by specifying the name of the project as a character string. You don't have to specify a path it will automatically create it in your current working directory, but you also have the option if you want to by setting the path argument.The function will create a README file, and also the needed folders for a project, that can be modified by the folders argument. The function also can initialise a Git repository and add important files to .gitignore, if the git argument was set to TRUE.

The following example creates a project with the **make_project** function:

```{r, eval=FALSE}

#Default: path set at the current working directory and doesn't initialise a Git repository
make_project("dsproject")

#Specification of arguments path and git:

make_project("dsproject", path = "~/Desktop/project", folders = c("figures", "documentation", "data", "reports", "R"),
                  readme = "README.md",
                  git = TRUE)

```

**Load and Attach Packages with use Function**


To load and attach a package with dsproject you can do it by using the **use** function. The **use** function provides a fast and user-friendly way, where you don't have to check if you have installed the package.If package is not installed, it asks if you want to install it, and if yes loads/attaches the package for your use. Else, it returns a message that the package is not installed.If the package does not exists, it returns FALSE and gives a warning. It checks and updates the list of currently attached packages and do not reload a namespace which is already loaded.

The following example loads and attach a package with the **use** function:

```{r, eval=FALSE}
#It can take a name:
use(dplyr)
#It can also take a character string:
use("dplyr")
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



